Heterogeneous Innovation and Intertemporal Productivity Choice

### 2018-02-19 Presentations/Proposal/SE-Proposal.tex

\documentclass[11pt]{beamer}
\usetheme{CambridgeUS}
\usecolortheme{lily}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{graphicx}
\usepackage{xcolor}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}
\usepackage[numbers]{natbib}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{dcolumn}
\captionsetup{skip=0.333\baselineskip}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\mc[1]{\multicolumn{1}{@{}c@{}}{#1}} % handy shortcut macro
\bibliographystyle{acm}
\author{Julio B. Roll}
\title{Heterogeneous Innovation and Intertemporal Productivity Choice}
%\subtitle{}
\setbeamercovered{transparent} 
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\setbeamercolor{frametitle}{fg=brightmaroon}
\setbeamercolor{title}{fg=brightmaroon}
\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
\date{February 5, 2018} 
%\subject{}

@@

\begin{frame}{Empirical Work - Patents}
How to discipline $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$?
	\begin{itemize}\itemsep12pt	
		\item USPTO patent data (e.g. \# patents, \# patent citations, if it's self-citation or external...).
		%data linked to Compustat
	\end{itemize}
Model (complete):
	\begin{itemize}
		\item Endogenous: R\&D, productivity (all parameters);
		\item Exogenous: labor market (wages, supply), consumers (discounting), mass of entrants;
		\item Estimated (for Patents): $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$;
		\item Calibrated (for Complete version): discounting, curvature of the R\&D cost function ($\eta$);
	\end{itemize}
\end{frame}

\begin{frame}{Empirical Work - Patents}
Estimation strategy:
	\begin{itemize}\itemsep12pt	
		\item Patent and citation distribution: invariant (at SS);
		\item Need to discipline patent arrival and quality ladder;
		\item Find the "decay rate" of patent quality;
		\item Distinguish external vs. internal (patent classification or type of citation, could do robustness), abrupt vs. incremental (\# of citations);
		\item Generational productivity step: impose the same shape and compare absolute levels ("envelope").
		%ideally: product cycle data
	\end{itemize}
\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usetheme{CambridgeUS}
\usecolortheme{lily}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{graphicx}
\usepackage{xcolor}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}
\usepackage[numbers]{natbib}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{dcolumn}
\captionsetup{skip=0.333\baselineskip}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\mc[1]{\multicolumn{1}{@{}c@{}}{#1}} % handy shortcut macro
\bibliographystyle{acm}
\author{Julio B. Roll \\ Scott Behmer}
\title{Heterogeneous Innovation and Intertemporal Productivity Choice}
%\subtitle{}
\setbeamercovered{transparent} 
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\setbeamercolor{frametitle}{fg=brightmaroon}
\setbeamercolor{title}{fg=brightmaroon}
\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
\date{February 14, 2018} 
%\subject{}

@@

\begin{frame}{Empirical Work - Patents}
How to discipline $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$?
	\begin{itemize}\itemsep12pt	
		\item USPTO patent data (e.g. \# patents, \# patent citations, if it's self-citation or external...).
		%data linked to Compustat
	\end{itemize}
Model (complete):
	\begin{itemize}
		\item Endogenous: R\&D, productivity (all parameters);
		\item Exogenous: labor market (wages, supply), consumers (discounting), mass of entrants;
		\item Estimated (for Patents): $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$;
		\item Calibrated (for Complete version): discounting, curvature of the R\&D cost function ($\eta$).
	\end{itemize}
\end{frame}

\begin{frame}{Empirical Work - Patents}
	\begin{center}
	\begin{figure}\centering\label{Innov7}
	\begin{minipage}[b]{0.45\linewidth}
	  \fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr.png}}}
	\end{minipage}
	\begin{minipage}[b]{0.45\linewidth}
		\fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr_cut.png}}}
	\end{minipage}
	\end{figure}
	\end{center}
	Summary: \# obs = 3,278,174; Mean = 11.76; Std. Dev. = 20.00
\end{frame}

\begin{frame}{Empirical Work - Patents}
GMM strategy:
	\begin{itemize}\itemsep12pt	
		\item Each patent in the data set can be classified as internal or external (based on whether the company has previous patents within that classification) and incremental versus abrupt (based on the number of citations that the patent has);
		\item Given a guess of parameter values $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$, we can calculate the moments;
		\item Potential moments to use: average rate of internal, abrupt patents; average rate of external, abrupt patents; average rate of internal, incremental patents; correlation between abrupt and incremental patent rates.
		%ideally: product cycle data
	\end{itemize}
\end{frame}
